Bayesian Neural Arithmetic Units -- Leveraging The Complex Plane

### 2020-04-07 paper/main.tex
cite diffeq+flux

\begin{abstract}
  Common Neural Networks poorly approximate simple arithmetic operations.  The
  new Neural Arithmetic Units aim to overcome this difficulty, but are limited
  either limited to operate on positive numbers (NALU by
  \citet{trask_neural_2018}), or can only represent simple addition and
  multiplication (NAU & NMU by \citet{madsen_neural_2020}).
  We present the first Neural Arithmetic Unit that operates on the full domain
  of real numbers and is capable of learning arbitrary power functions.
  For a theoretically grounded sparsification of the units we employ Bayesian
  compression on the model weights via Automatic Relevance Determination.
\end{abstract}

@@

>>>>

\begin{abstract}
  Common Neural Networks poorly approximate simple arithmetic operations.  The
  new Neural Arithmetic Units aim to overcome this difficulty, but are limited
  either limited to operate on positive numbers (NALU by
  \citet{trask_neural_2018}), or can only represent simple addition and
  multiplication (NAU \& NMU by \citet{madsen_neural_2020}).
  We present the first Neural Arithmetic Unit that operates on the full domain
  of real numbers and is capable of learning arbitrary power functions.
  For a theoretically grounded sparsification of the units we employ Bayesian
  compression on the model weights via Automatic Relevance Determination.
\end{abstract}

@@

% TODO: put this in acknowledgements %
all the results in this paper were create with the help of the following Julia
packages: \cite{rackauckas_differentialequationsjl_2017} + (Flux.jl)
